### 2017-12-30 README.Rmd
Add covr

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)

>>>>

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage status](https://codecov.io/gh/andrewpbray/infer//branch/master/graph/badge.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
